Interactive Visual Analysis of Image-Centric Cohort Study Data

### 2014-06-24 draft.tex
fixed error in visualization figure and other stuff

Morphometric features are derived to allow for statistical comparison of the tissue, which incorporates mostly positions, diameters, volumes and relative distances and alignment to other structures.
%-------------------------------- Figure --------------------------------
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.3in]{figures/InteractionLoop}
 \caption{Detailed \emph{IVA Loop} as extension from Figure~\ref{fig:WorkflowComparison}.
 %
 Usually starting with a selection of a feature of interest (user-driven or via data mining techniques), the data are mapped using a visualization technique appropriate for the selected data types.
 %
 The data are visualized in the range and domain space, which can then be brushed, yielding new groups, to be investigated using further features.
 %
 Note that adjacent steps are directly connected via feedback loops allowing for an iterative refinement and giving as much freedom to the user as possible.}
 \label{fig:InteractionLoop}
\end{figure}
%------------------------------ / Figure --------------------------------
\subsection{Analysis Workflow}
%-------------------------------- Figure --------------------------------
\begin{figure*}[htb]
 \centering
 %\includegraphics[width=1.5in]{figures/InteractionLoop}
 % \includegraphics[width=3.5in]{figures/visualization}
 %\includegraphics[width=1\textwidth]{figures/visualization}
 \includegraphics[width=1\textwidth, resolution=300]{figures/visualization}
 \caption{\com{Add: Explanation of the color coding, ToDo: Selektion in Abbildung 3 einbauen und daran Selektion erklären}
 %
 (Left) Screenshot from the front-end, which is divided as follows: (a) The sidebar containing all features as well as the groups defined in the analysis process; (b) the canvas area where features can be added via drag and drop and the visualization is chosen automatically according to the data type; (c) the interactive pivot table showing the exact numbers for each displayed feature combination.
 %
 The data displayed is used to analyze the lumbar spine. Features can be added freely on the canvas via drag and drop.
 %
 Dropping the \emph{gender} parameter on the already plotted \emph{body size} container creates a mosaic plot combining both features (right).
 %
 \com{3d-Koordinatensystem Kodierung durch Farbe (grün, rot, nuancen)}
 %The lumbar spine models encode distance to the mean model using  \emph{color} 
 }
 \label{fig:visualization}
\end{figure*}
%-------------------------------- /Figure -------------------------------
Our proposed \emph{IVA} workflow consists of three major steps as illustrated in Figure~\ref{fig:InteractionLoop}: Feature selection, visualization and brushing.
%
A hypothesis-driven analysis usually starts with the selection of features, or shape groups derived from a shape-based clustering.
%
\emph{Hypothesis generation} with focus on image data starts with a shape-based clustering.
%
\com{ToDo: Multivariate analysis using the adjacency matrix may have also be explained here, depending on the Application chapter.}
%
The feature is mapped using an automatically chosen visualization appropriate for its data type (described in detail in the following section).
%
The visualization techniques have to combine both image-and non-image data in order to set domain and range data in relation to each other.
%
In our system, the visualization can either be brushed or new features can be added to the analysis. 
%
Brushing methods are subdivided using the previously described \emph{IVA} patterns.
%
Brushed regions are treated like features, as they divide the subject space just like categorical features.
%
Selecting features also triggers a \emph{multivariate analysis} using contingency values (described in the following section) to highlight features associated with selected features.
%
A sample workflow using interaction and visualization techniques described in the next section can be seen in Figure~\ref{fig:visualization}.

>>>>

Morphometric features are derived to allow for statistical comparison of the tissue, which incorporates mostly positions, diameters, volumes and relative distances and alignment to other structures.
%-------------------------------- Figure --------------------------------
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.3in]{figures/InteractionLoop}
 \caption{Detailed \emph{IVA Loop} as extension from Figure~\ref{fig:WorkflowComparison}.
 %
 Usually starting with a selection of a feature of interest (user-driven or via data mining techniques), the data are mapped using a visualization technique appropriate for the selected data types.
 %
 The data are visualized in the range and domain space, which can then be brushed, yielding new groups, to be investigated using further features.
 %
 Note that adjacent steps are directly connected via feedback loops allowing for an iterative refinement and giving as much freedom to the user as possible.}
 \label{fig:InteractionLoop}
\end{figure}
%------------------------------ / Figure --------------------------------
\subsection{Analysis Workflow}
%-------------------------------- Figure --------------------------------
\begin{figure*}[htb]
 \centering
 %\includegraphics[width=1.5in]{figures/InteractionLoop}
 % \includegraphics[width=3.5in]{figures/visualization}
 %\includegraphics[width=1\textwidth]{figures/visualization}
 \includegraphics[width=1\textwidth, resolution=300]{figures/visualization}
 \caption{
 %
 (Left) Screenshot from the front-end, which is divided as follows: (a) The sidebar containing all features as well as the groups defined in the analysis process; (b) the canvas area where features can be added via drag and drop and the visualization is chosen automatically according to the data type; (c) the interactive pivot table showing the exact numbers for each displayed feature combination; \add{(d) Buttons to open panes containing the contingency matrix, contingency pane and pivot table}.
 %
 The data displayed is used to analyze the lumbar spine. Features can be added freely on the canvas via drag and drop.
 %
 Dropping the \emph{gender} parameter on the already plotted \emph{body size} container creates a mosaic plot combining both features (right).
 %
 \add{In a prior step, the user selected all subjects with diagnosed thyroid disorder.
 %
 These subjects are shown as shade in the visualization, denoting their share.
 %Their shares are denoted in the bar chart as blue and the mosaic plot as dark shade.
 %
 Subjects between 153.5--170~cm body size are more affected by thyroid disorder (box plot) and are mostly female (mosaic plot).}
 %
 \add{Distance to the mean mesh of subjects with thyroid disorder is encoded as red for x axis, blue to y axis and green to z axis.}
 %The lumbar spine models encode distance to the mean model using  \emph{color} 
 }
 \label{fig:visualization}
\end{figure*}
%-------------------------------- /Figure -------------------------------
Our proposed \emph{IVA} workflow consists of three major steps as illustrated in Figure~\ref{fig:InteractionLoop}: Feature selection, visualization and brushing.
%
A hypothesis-driven analysis usually starts with the selection of features, or shape groups derived from a shape-based clustering.
%
\emph{Hypothesis generation} with focus on image data starts with a shape-based clustering.
%
\com{ToDo: Multivariate analysis using the adjacency matrix may have also be explained here, depending on the Application chapter.}
%
The feature is mapped using an automatically chosen visualization appropriate for its data type (described in detail in the following section).
%
The visualization techniques have to combine both image-and non-image data in order to set domain and range data in relation to each other.
%
In our system, the visualization can either be brushed or new features can be added to the analysis. 
%
Brushing methods are subdivided using the previously described \emph{IVA} patterns.
%
Brushed regions are treated like features, as they divide the subject space just like categorical features.
%
Selecting features also triggers a \emph{multivariate analysis} using contingency values (described in the following section) to highlight features associated with selected features.
%
A sample workflow using interaction and visualization techniques described in the next section can be seen in Figure~\ref{fig:visualization}.
